Pillar 2 - Topic Modeling

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
get topic terms

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```
#DELETE LATERRRRRRRRRRRRRRRRRRRRRRRRRRRRRR
Include d_course
```{r d_course}
load("Output/data_general.RDATA")

rm(d_AoD, d_assessment, d_ILO, list_AoD_assessment)
```
# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

@@

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
##Functions for models (get gamma, get beta, extract_dtm)
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

@@

```{r LDA fit, cache = TRUE, eval = TRUE}

@@

##Model Evaluation
###Plots
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(){

@@

    #Wrangling
    select(n_topic, Origin, Perplexity, LogLikelihood) %>%

    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%

    #Graphics
    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
    geom_point() +
    facet_wrap(`Eval Type` ~ Origin, scales = "free") +
    theme_minimal()

@@

#Plot
plot_evaluation()
```

##Saving filed for different sessions
For internal use:
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" )
```

#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

@@

inspect_topics <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta)

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

>>>>

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

# TF-IDF
## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

@@

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
###Functions for models (get gamma, get beta, extract_dtm)
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

@@

```
###Training Models
```{r LDA fit, cache = TRUE, eval = TRUE}

@@

##Model Evaluation
###Plots
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

@@

    #Wrangling
    select(n_topic, Origin, Perplexity, LogLikelihood) %>%
    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
    filter(Origin == origin) %>%

    #Graphics
    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
    geom_point() +
    geom_line() +
    facet_grid(rows = vars(`Eval Type`), scales = "free") +
    theme_minimal()

@@

#Plot
plot_evaluation("overview")
plot_evaluation("manuals")
```

##Saving model_data:
For internal use:
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
```

#Distributions
#NOTE: select how many topics to use

##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

@@

# FUNCTION
#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
get_top_match <- function(d_distribution){
  print(!!sym(d_distribution))
}
Hi <- "hello"
get_top_match(Hi)

get_top_terms_topic <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term))

@@

get_top_topics_course <- function(d_gamma){
  data.frame(d_gamma) %>%
    group_by(document) %>%
    top_n(5, gamma) %>%
    select(document, topic) %>%
    summarise(top_topic = list(topic))
}

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term)) %>%
    select(top_words) %>%
    collapse(top_words)
}
#Saving to models
test_topic_model <-  test_topic_model %>%
  mutate(top_terms_topic = map(Beta, .f = get_top_terms_topic))

test_topic_model <- test_topic_model %>%
  mutate(top_topic_course = map(Gamma, .f = get_top_topics_course))

```
#App
##Selectig keywords
```{r key words}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

go_down <- function(my_list, i){
  my_list[[i]]
}

get_key_words <-  function(d_top_words){

  select(top_words) %>%
    top_n(5)
}

View(test_topic_model)

a <- test_topic_model[["top_terms_topic"]]

d_top_words <- a[1]

#mutate(kw = get_key_words(top_terms_topic)) 
d_top_words <- a$top_terms_topic

kw <- lapply(
  distribution$beta,
  get_top_words
)

```
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")
